# Running the analysis


```{r}
# Let's specify the packages needed
library(reshape2) ## for the 'melt' function
library(nlme) ## for our multivariate model

# Let's set our working directory
setwd()

# Load in our data
coroutcomes <- read.csv(file = "coroutcomes.csv", header = TRUE)

# Convert our data into a format relevant for multivariate analysis
coroutcomes_melt <- melt(hippocomplete2_long[, c(".imp", "id", "AgeMRI7T", "sex", "ZICV_mm3", "socsup3","depsymptoms", "emo_ab", "psy_ab", "phys_ab", "sex_ab", "LE", "BAI_cat1", "child_mal", "ZCA1sum", "ZCA2sum", "ZCA3sum", "ZDGsum", "ZERCsum", "ZSUBsum", "ZTailsum", "Zbrain_corrected_mm3", "brain_corrected_mm3", "Tailsum", "SUBsum", "ERCsum", "DGsum", "CA3sum", "CA2sum", "CA1sum", "ZHIPPsum", "HIPPsum", "HIPP_L", "HIPP_R")], measure.vars = c("ZCA1sum", "ZCA2sum", "ZCA3sum", "ZDGsum", "ZERCsum", "ZSUBsum", "ZTailsum"))
```

Here, we are telling R to select our outcomes, that is, seven hippocampal subfields, "ZCA1sum", "ZCA2sum", "ZCA3sum", "ZDGsum", "ZERCsum", "ZSUBsum", "ZTailsum" and creating a new categorical variable called "variable" for them as well as our new outcome variable "value" that holds the values for all subfields.

```{r}
# Model building

socialsupport <- gls(value ~ -1 + variable + variable:factor(socsup3) + variable:AgeMRI7T +
                       variable:sex + variable:ZICV_mm3, data = coroutcomes_melt, method = "ML",
                     correlation=corSymm(form = ~1 | id), weights = varIdent(form = ~1 | variable))
```

Here, we add '-1' to withhold the intercept for ease of interpretation. We add here our main predictor, in this case social support or 'socsup3', as well as our covariates: age, sex, and intracranial volume. We specify an unstructured correlation matrix per individual ('id') and for each outcome ('variable').

Now let's compare our results to performing a univariate analysis:
```{r}
socialsupport.univariate <- lm(ZCA1sum ~ factor(socsup3) + AgeMRI7T + sex + ZICV_mm3, data = coroutcomes)
```

Let's compare our estimates:
```{r}

```

As we see here, our univariate analysis resulted in larger standard errors than our multivariate analysis that considers the correlation between outcomes. Therefore, we see more precision and less probability of making a type-I error.

I hope this tutorial was helpful for you and inspires you to consider performing multivariate analyses over univariate ones when your outcomes are correlated!

Cheers!

-	Emma